The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-20 paper/discussion.tex
make Guo+2017 reference more precise

\paragraph{The hot Jupiter rate discrepancy}
There is at least one context in which ignoring binarity may already be 
leading to discrepant measurements.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
The discrepancy has weak statistical significance ($<3\sigma$).
One reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant 
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
The {\it Kepler}\ sample specifically has been measured to be more metal poor 
than the local neighborhood, with a mean metallicity of $[{\rm M/H}]_{\rm 
    mean}\approx -0.05$~\citep{dong_metallicities_2014,guo_metallicity_2017}.
Studying the problem in detail, \citeauthor{guo_metallicity_2017}\! recently 
argued that the metallicity difference could account for a $\approx 20\%$ 
relative difference in the measured rates between the CKS and {\it Kepler}\ 
samples~--~not a factor of two.
\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
binary contamination and imperfect stellar properties'' must also be at play.

>>>>

\paragraph{The hot Jupiter rate discrepancy}
There is at least one context in which ignoring binarity may already be 
leading to discrepant measurements.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
Though the discrepancy has weak statistical significance ($<3\sigma$),
one reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant 
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
Investigating the discrepancy from the metallicty 
angle,~\citet{guo_metallicity_2017} measured the
{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
-0.045\pm0.009$, which is lower than the California Planet Search's mean of 
$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
The former value agrees with that measured by \citet{dong_metallicities_2014}.
Based on their measurements, \citeauthor{guo_metallicity_2017}\! 
then argued that the metallicity difference could account for a $\approx 20\%$ 
relative difference in the measured rates between the CKS and {\it Kepler}\ 
samples~--~not a factor of two.
\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
binary contamination and imperfect stellar properties'' must also be at play.
